---
title: "InVideo TikTok Stats Study"
author: ""
date: "Last updated on `r Sys.Date()`"
output:
  html_document:
    theme: paper
    highlight: kate
    code_folding: hide
    toc: true
    toc_depth: 3
    toc_float: true
editor_options: 
  chunk_output_type: inline
---

```{=html}
<style>
.list-group-item.active, .list-group-item.active:hover, .list-group-item.active:focus {
  background-color: #00d188;
  border-color: #00d188;
}

body {
  font-family: montserrat;
  color: #444444;
  font-size: 14px;
}

h1 {
  font-weight: bold;
  font-size: 28px;
}

h1.title {
  font-size: 30px;
  color: #00d188;
}

h2 {
  font-size: 24px;
}

h3 {
  font-size: 18px;
}
</style>
```
```{r message=FALSE, warning=FALSE}
rm(list=ls())
## packages: remove or add your necessary packages

required_packages <- c("tidyverse", "readxl", "ggthemes", "hrbrthemes", "extrafont", "plotly", "scales", "stringr", "gganimate", "here", "tidytext", "sentimentr", "scales", "DT", "here", "sm", "mblm", "glue", "fs", "knitr", "rmdformats", "janitor", "urltools", "colorspace", "pdftools", "showtext", "stringi", "fmsb", "lemon")

for(i in required_packages) { 
if(!require(i, character.only = T)) {

  #  if package is not existing, install then load the package
install.packages(i, dependencies = T)
require(i, character.only = T)
}}

remotes::install_github("gadenbuie/tiktokrmd")
library(tiktokrmd)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE, fig.showtext = TRUE, dpi = 700)

knitr::knit_hooks$set(inline = function(x) {
  prettyNum(x, big.mark = ",", small.mark = ",", scientific = F)
})

Sys.setlocale("LC_TIME", "C")
extrafont::loadfonts(device = "win")
```

```{r plot_settings, message=FALSE, warning=FALSE}

## save plots?
save <- TRUE
#save <- FALSE

## quality of png's
dpi <- 750

## font adjust; please adjust to client´s website
#extrafont::loadfonts(device = "win", quiet = TRUE)
#font_add_google("Montserrat", "Montserrat")
# font_add_google("Overpass", "Overpass")
# font_add_google("Overpass Mono", "Overpass Mono")



## theme updates; please adjust to client´s website
#theme_set(ggthemes::theme_clean(base_size = 15))
theme_set(ggthemes::theme_clean(base_size = 15, base_family = "Montserrat Light"))


theme_update(plot.margin = margin(30, 30, 30, 30),
             plot.background = element_rect(color = "white",
                                            fill = "white"),
             plot.title = element_text(size = 20,
                                       face = "bold",
                                       lineheight = 1.05,
                                       hjust = .5,
                                       margin = margin(10, 0, 25, 0)),
             plot.title.position = "plot",
             plot.caption = element_text(color = "grey40",
                                         size = 9,
                                         margin = margin(20, 0, -20, 0)),
             plot.caption.position = "plot",
             axis.line.x = element_line(color = "black",
                                        size = .8),
             axis.line.y = element_line(color = "black",
                                        size = .8),
             axis.title.x = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(t = 20)),
             axis.title.y = element_text(size = 16,
                                         face = "bold",
                                         margin = margin(r = 20)),
             axis.text = element_text(size = 11,
                                      color = "black",
                                      face = "bold"),
             axis.text.x = element_text(margin = margin(t = 10)),
             axis.text.y = element_text(margin = margin(r = 10)),
             axis.ticks = element_blank(),
             panel.grid.major.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.major.y = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.x = element_line(size = .6,
                                               color = "#eaeaea",
                                               linetype = "solid"),
             panel.grid.minor.y = element_blank(),
             panel.spacing.x = unit(4, "lines"),
             panel.spacing.y = unit(2, "lines"),
             legend.position = "top",
             legend.title = element_text(family = "Montserrat",
                                         color = "black",
                                         size = 14,
                                         margin = margin(5, 0, 5, 0)),
             legend.text = element_text(family = "Montserrat",
                                        color = "black",
                                        size = 11,
                                        margin = margin(4.5, 4.5, 4.5, 4.5)),
             legend.background = element_rect(fill = NA,
                                              color = NA),
             legend.key = element_rect(color = NA, fill = NA),
             #legend.key.width = unit(5, "lines"),
             #legend.spacing.x = unit(.05, "pt"),
             #legend.spacing.y = unit(.55, "pt"),
             #legend.margin = margin(0, 0, 10, 0),
             strip.text = element_text(face = "bold",
                                       margin = margin(b = 10)))

## theme settings for flipped plots
theme_flip <-
  theme(panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_line(size = .6,
                                          color = "#eaeaea"))

## theme settings for maps
theme_map <- 
  theme_void(base_family = "Montserrat") +
  theme(legend.direction = "horizontal",
        legend.box = "horizontal",
        legend.margin = margin(10, 10, 10, 10),
        legend.title = element_text(size = 17, 
                                    face = "bold"),
        legend.text = element_text(color = "grey33",
                                   size = 12),
        plot.margin = margin(15, 5, 15, 5),
        plot.title = element_text(face = "bold",
                                  size = 20,
                                  hjust = .5,
                                  margin = margin(30, 0, 10, 0)),
        plot.subtitle = element_text(face = "bold",
                                     color = "grey33",
                                     size = 17,
                                     hjust = .5,
                                     margin = margin(10, 0, -30, 0)),
        plot.caption = element_text(size = 14,
                                    color = "grey33",
                                    hjust = .97,
                                    margin = margin(-30, 0, 0, 0)))

## numeric format for labels
num_format <- scales::format_format(big.mark = ",", small.mark = ",", scientific = F)

## main color backlinko
bl_col <- "#00d188"
bl_dark <- darken(bl_col, .3, space = "HLS")

## colors + labels for interval stripes
int_cols <- c("#bce2d5", "#79d8b6", bl_col, "#009f66", "#006c45", "#003925")
int_perc <- c("100%", "95%", "75%", "50%", "25%", "5%")

## colors for degrees (Bachelors, Massters, Doctorate in reverse order)
cols_degree <- c("#e64500", "#FFCC00", darken(bl_col, .1))

## gradient colors for position
colfunc <- colorRampPalette(c(bl_col, "#bce2d5"))
pos_cols <- colfunc(10)
```

```{r message=FALSE, warning=FALSE}
brands = read_csv("../raw_data/brands_list.csv", col_types="cciccddddddd")
top_videos = read_csv("../raw_data/top_videos.csv", col_types="cicddddcc")
annotations = read_csv("../raw_data/video_annotations.csv", col_types="")
```

```{r message=FALSE, warning=FALSE}
# Aggregate similar categories into one
brands = brands %>%
  mutate(
  category = ifelse(category %in% c("Tech", "IT Services"), "Tech & IT", 
    ifelse(category %in% c("Restaurants", "Soft Drinks", "Food", "Beers", "Spirits"), "Food & Beverages",
    ifelse(category %in% c("Healthcare", "Pharma"), "Healthcare & Pharma", 
    ifelse(category == "Cosmetics & Personal Care", "Cosmetics", category)
  )))) %>%
  filter(brand_name != "Queen City Alchemy")
```

```{r message=FALSE, warning=FALSE}
# Filter out brands with no account, fans, or posts
# And compute some aggregations/averages
brands_with_posts = brands %>%
  filter(!is.na(tiktok_handle)) %>%
  filter(!is.na(fans)) %>%
  filter(!is.na(total_posts)) %>%
  mutate(avg_views = total_views/total_posts) %>% # Average views per post
  mutate(total_engagement = total_likes + total_comments + total_shares) %>% # Engagement = Likes + Shares + Comments
  mutate(avg_engagement = total_engagement/total_posts) # Avg. engagement per post
```

```{r}
## Changing variable in thousands to have actual values
top_videos = top_videos %>% 
    mutate_at(vars(contains('_000s')), ~ .*1000)

change_colnames = function(s) {
  paste(s)
  ifelse((str_sub(s, -5) == "_000s"), str_sub(s, 1, -6), s)
}

top_videos = top_videos %>% 
  rename_with(change_colnames)
```

```{r}
boolean_cols = colnames(annotations)[-1:-6]

annotations = annotations %>% 
  filter_all(any_vars(!is.na(.))) %>% # Removes rows where all the variables are NA
  mutate_at(boolean_cols, ~ifelse(is.na(.), FALSE, TRUE))
```

```{r}
## Fixing data quality issue
annotations = annotations %>%
  mutate(uses_sex = ifelse(
    str_detect(link, "@victoriassecret"),
    TRUE,
    uses_sex
  ))
```

# TikTok Guide for Businesses (2021)

**[TODO: Other title suggestions]**

With over 2 billion downloads and over 1 billion monthly active users, TikTok has marked itself as one of the biggest social media platform in just a couple of years.

And while the platform itself enjoys immense popularity, especially among Gen Z users, businesses have been slow to expand to their social media marketing machines to the nascent video sharing platform.

To help you tailor your TikTok marketing strategy, we studied over 300 brands and more than 650 videos from the top TikTok brands to figure out how companies like Amazon, Apple, Samsung, and Chevrolet manage their TikTok presence and what works on the platform and what doesn't.

Specifically, we looked at

-   which of the most valuable brands had a TikTok presence
-   how often these brands were posting on TikTok
-   channel and video-level metrics for these brands
-   what the style, tone, and design of the best performing TikTok videos were.

Without further ado, let's dive into what we found.

[**TODO:** Move Key Takeaways from the bottom to here. It's there now because it depends on the code and putting it here would cause errors.]

[**TODO:** Add methodology section here or at the bottom. Do you have a preference?]

## Half of the Top Brands Don't Have a TikTok Presence Yet

Of the 317 brands we studied, nearly **50% either didn't have a TikTok account or had zero posts** on their account. This included billion-dollar brands like Google, Facebook, YouTube, IKEA, Nestlé, Audi, Toyota, and more.

That's a rather significant gap in the market and **establishing an early TikTok presence** can be the source of a **major marketing advantage** for your brand and potentially even allow you to leapfrog much larger brands who've simply ignored the platform so far.

```{r}
counts = as.integer(c(
brands %>% 
  count(),

brands %>% 
  filter(is.na(tiktok_handle)) %>%
  count(),

brands %>%
  filter(is.na(total_posts)) %>%
  count(),

brands %>%
  filter(is.na(fans)) %>%
  count()
))

data = bind_cols(label=c("Brands studied", "Brands without a TikTok account", "Brands with no posts", "Brands with no followers"), counts=counts)

data %>%
  arrange(counts) %>%
  mutate(counts = 100*counts/dim(brands)[1]) %>%
  mutate(label=factor(label, levels=label)) %>%
  ggplot(aes(x=label, y=counts)) +
    geom_segment(aes(xend=label, yend=0)) +
    geom_point( size=4, color="orange") +
    coord_flip() +
    labs(title="50% of the major brands have no TikTok presence", x=NULL, y="% of brands")
```

## The best brands post around 3 times per week

As with YouTube, TikTok's algorithm rewards frequent and consistent posts. We found that, on average, the best-performing TikTok brands (those with 1 million or more average views per post) released a **new video 3.16 times per week**.

[**TODO for Laura:** Add a pill box with the 3.16 times number likes [this image](https://mk0apibacklinkov1r5n.kinstacdn.com/app/uploads/2020/08/the-average-time-to-first-click-is-about-15-seconds-960x346.png)]

While doing more than 5 posts per week is likely not going to make much of a difference, there are exceptions.

```{r, include=FALSE}
# brands_with_posts %>%
#   filter(brand_name != "Queen City Alchemy") %>%
#   # filter(avg_posts_per_week <= 10) %>% 
#   ggplot(aes(x=avg_posts_per_week, y=avg_views)) +
#     geom_point() +
#     geom_smooth(method="lm") +
#     scale_y_log10()

thresh = 1e4

avg_posts_summary = brands_with_posts %>%
  filter(brand_name != "Queen City Alchemy") %>%
  filter(!is.na(avg_posts_per_week)) %>%
  filter(total_posts >= 5) %>%
  filter(avg_views >= thresh) %>%
  summarise(
    mean_weekly_posts = mean(avg_posts_per_week), 
    min_weekly_posts = min(avg_posts_per_week), 
    max_weekly_posts = max(avg_posts_per_week),
    median_weekly_posts = median(avg_posts_per_week)
  )
avg_posts_summary
```

```{r}
brands_with_posts %>%
  filter(brand_name != "Queen City Alchemy") %>%
  filter(!is.na(avg_posts_per_week)) %>%
  filter(total_posts >= 5) %>%
  filter(avg_views >= thresh) %>%
  mutate(avg_posts_per_week = as.integer(avg_posts_per_week)) %>%
  group_by(avg_posts_per_week) %>%
  count() %>%
  ggplot(aes(x=avg_posts_per_week, y=n)) +
    geom_col() +
    labs(x="Avg. posts per week", y="Number of brands", title="Most brands post less than 5 times per week")
```

Over to the very right of the graph is Amazon Prime Video, which not only posts more than 40 times per week but also draws an average of 1.32 million views per post.

These are mostly snippets and previews of its current and upcoming shows, however, and it's unlikely that most business will have as much content as the streaming platform.

[**TODO: change title of plot**]

```{r}
brands_with_posts %>%
  filter(brand_name %in% c("Netflix", "Amazon Prime Video")) %>%
  mutate(total_views = total_views/1e6) %>%
  ggplot(aes(x=brand_name, y=total_views)) +
    geom_col() +
    labs(title="Consistency makes a big difference", x=NULL, y="Total views (millions)")

# brands_with_posts %>%
#   filter(brand_name %in% c("Netflix", "Amazon Prime Video")) %>%
#   # mutate(total_views = total_views/1e6) %>%
#   select(brand_name, total_posts, total_views, total_likes, total_comments, total_shares, avg_views, avg_engagement) %>%
#   pivot_longer(!brand_name, names_to="metric", values_to="value") %>%
#   # mutate(value = value/1e6) %>%
#   ggplot(aes(
#     x=ifelse(brand_name == "Netflix", -value, value),
#     y = metric, fill = brand_name)
#   ) +
#     geom_col() +
#     scale_x_symmetric(labels = abs) +
#     scale_x_log10() +
#     labs(x = "Population")
```

Interestingly, the only other brand that could take Amazon Prime on, Netflix, posts far less often (8.5 times per week) and the difference shows. While Netflix's TikTok account has accumulated a total of 419M views, Amazon Prime sits at a pretty 2.2 trillion views, largely because of its more consistent rate of posting.

**Key Takeaway:** post at least three times a week and make sure to be more frequent and consistent than your competitors.

## How many views is a single follower worth?

The number of followers a brand has is, of course, highly correlated with the average views and engagement their posts generate.

The larger your audience, the more likely you are to get shares, likes, and comments for your videos. In short, going viral is easier with a larger following, and building a large and dedicated fan base should be one of the top priorities for your channel.

This begs the question, though: just how important is gaining one additional follower? Say you could run a giveaway which cost you \$X to get one more follower. What would the return on investment for that money be? Can we quantify that?

**[TODO: chart title]**

```{r}
reg = lm(log10(avg_views) ~ log10(fans), data=brands_with_posts)
fans_avg_views_slope = round(coefficients(reg)[2], 2)

brands_with_posts %>%
  ggplot(aes(x=fans, y=avg_views)) +
    geom_point() +
    geom_smooth(method="lm", formula=y~x, se=FALSE) +
    scale_x_log10(
      breaks=c(1e2, 1e4, 1e6, 1e8),
      labels=c("100", "10K", "1M", "100M")
    ) +
    scale_y_log10(
      breaks=c(1e3, 1e4, 1e5, 1e6, 1e7),
      labels=c("1K", "10K", "100K", "1M", "10M")
    ) +
    labs(
      x="Number of followers", 
      y="Avg. views per post",
      title="How many views is a single follower worth?"
    )
```

Thankfully for you, we did just that, and based on the regression line you see above, a **1% increase in followers corresponds to a `r fans_avg_views_slope`% increase in average views per post**.

Say you currently have 100 followers and you ran a \$500 giveaway to get an additional 20 followers. That's a 20% increase in followers and you can expect, in return, an approximately `r 20*fans_avg_views_slope`% increase in the number of views your posts generate.

## Tech, Food, and Gaming brands perform the best on TikTok

Next, we wanted to look at which types of brands performed the best on TikTok. So, we computed the average number of views each brand got on their videos and then found the average of this average for the different types of industries each brand belonged to.

```{r}
# brands_with_posts %>%
#   ggplot(aes(x=fans, y=avg_views, color=category)) +
#     geom_point() +
#     scale_x_log10() +
#     scale_y_log10()

brands_with_posts %>%
  group_by(category) %>%
  summarise(avg_views_per_video_per_category = mean(avg_views)) %>%
  arrange(avg_views_per_video_per_category) %>%
  tail(10) %>%
  mutate(category=factor(category, levels=category)) %>%
  ggplot(aes(x=category, y=avg_views_per_video_per_category)) +
    geom_segment( aes(xend=category, yend=0)) +
    geom_point( size=4, color="orange") +
    coord_flip() +
    labs(title="How popular are different types of brands?", x=NULL, y="Avg. views per video") +
    scale_y_continuous(
      labels=c("0", "500K", "1M", "1.5M", "2M"),
      breaks=c(0, 5e5, 1e6, 1.5e6, 2e6),
      expand=c(0, 0, 0.05, 0)
    )
```

The results showed that Tech & IT brands seemed to perform the best, drawing more than 2.3 million views per post, followed by Food & Beverages, Gaming, and Media.

That's not to say that you need to be a billion-dollar tech company to be successful on TikTok. As with other social media platforms, TikTok rewards creativity far more than anything else.

```{r}
brands_with_posts %>% 
  filter(total_posts > 5) %>%
  group_by(brand_name) %>% 
  summarise(category=category, avg = mean(avg_views)) %>% 
  arrange(avg) %>%
  tail(10) %>%
  mutate(brand_name = ifelse(brand_name =="World Health Organization", "WHO", brand_name)) %>%
  mutate(brand_name = ifelse(brand_name =="sosatisfying", "So Satisfying", brand_name)) %>%
  mutate(brand_name=factor(brand_name, levels=brand_name)) %>%
  ggplot(aes(x=brand_name, y=avg)) +
    geom_segment( aes(xend=brand_name, yend=0)) +
    geom_point(aes(x=brand_name, y=avg, color=category),size=4, inherit.aes=FALSE) +
    coord_flip() +
    labs(
      title="The 10 Most Popular TikTok Brands", 
      x=NULL, 
      y="Avg. views per video",
      color="Industry"
    ) +
  scale_y_continuous(
    breaks=c(0, 5e6, 1e7, 1.5e7),
    labels=c("0", "5M", "10M", "15M"),
    expand=c(0, 0, 0.1, 0)
  ) + theme(legend.position="right")
    # scale_y_continuous(
    #   labels=c("0", "500K", "1M", "1.5M", "2M"),
    #   breaks=c(0, 5e5, 1e6, 1.5e6, 2e6)
    # )
```

In fact, the most popular TikTok brand that we studied was So Satisfying, whose videos generate 14M videos on average and they're all about making the most mundane of things look sexy. Here's their best performing video (with 76 million views!) about a particularly interesting type of shoe:

```{r}
tiktok_embed("https://www.tiktok.com/@sosatisfying/video/6828726014307257606")
```

It's not all that surprising to see TikTok made the cut. In fact, 5 of the top 10 videos by views were from TikTok's own account. Since we were only studying the 5 most viewed videos from each brand, that's basically a 100% success rate.

So, if you're going to take your TikTok cues from any single brand, go check out \\@TikTok --- after all, they made the platform!

But another interesting addition to the list is the World Health Organization. Sure, the ongoing pandemic has probably contributed significantly to their popularity, but they are, nonetheless, a great example of a non-profit using TikTok to run social awareness campaigns --- and not just about COVID-19.

Here's a great video from the WHO about the tobacco industry and the dangers of smoking in general. The video drew over 54 million views and is an excellent example of a voiceover video with some really amazing video editing and graphics to boot:

```{r}
tiktok_embed("https://www.tiktok.com/@who/video/6832233774097517830")
```

## Music Makes the Video

TikTok videos thrive on music. Of the nearly 650 videos we studied, nearly 80% of the posts had music.

[**TODO for Laura:** Create a graphic like [this one](https://mk0apibacklinkov1r5n.kinstacdn.com/app/uploads/2020/08/42-percent-of-local-searchers-click-on-the-google-map-pack-960x430.png)]

```{r music}
annotations %>%
  mutate(has_music = ifelse(music_type == "No music", "No music", "Has Music")) %>%
  group_by(has_music) %>%
  count() %>%
  ungroup() %>%
  arrange(n) %>%
  mutate(frac = n/sum(n)) %>%
  mutate(ymax = cumsum(frac)) %>%
  mutate(ymin = lag(ymax)) %>%
  mutate(ymin = ifelse(is.na(ymin), 0, ymin)) %>%
  mutate(label = paste0(has_music, ": ", 100*round(frac, 2), "%")) %>%
  mutate(label_position = (ymax + ymin)/2) %>%
  ggplot(aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3, fill=has_music)) +
    geom_rect() +
    geom_label( x=3.5, aes(y=label_position, label=label), size=6) +
    scale_fill_brewer(palette=8) +
    coord_polar(theta="y") +
    xlim(c(2, 4)) +
    theme_void() +
    theme(legend.position = "none")
```

Additionally, it seems that upbeat music is by far the most popular choice, which isn't all that surprising when you consider that TikTok owes a large part of its popularity to dance videos.

[**TODO:** Choose chart title from two options]

```{r}
annotations %>%
  group_by(music_type) %>%
  count() %>%
  ungroup() %>%
  mutate(n = 100*n/sum(n)) %>%
  ggplot(aes(x=music_type, y=n)) +
    geom_col() +
    labs(
      title="Upbeat music is by far the most popular\n OR \n How popular are different types of music",
      x=NULL,
      y=NULL
    ) +
    scale_y_continuous(
      labels=c("0%", "20%", "40%", "60%"),
      breaks=c(0, 20, 40, 60)
    )
```

```{r}
music_df = annotations %>%
  group_by(music_type) %>%
  count() %>%
  bind_rows(
    annotations %>%
      mutate(music_type = ifelse(music_type == "No music", "No music", "Has Music")) %>%
      group_by(music_type) %>%
      count()
  ) %>%
  ungroup() %>%
  mutate(frac = n/dim(annotations)[1])

upbeat_over_has_music = music_df %>% filter(music_type == "Upbeat") %>% select(n) / music_df %>% filter(music_type == "Has Music") %>% select(n)
```

Add some music and even something as mundane as you cutting grass can attract 20.9M views. In fact, the folks at Adrlich Landscape have made a whole channel around this --- and they're doing extremely well on the platform. Just goes to show that you don't need to be a multi-billion dollar business to succeed on social media; a little bit of creativity goes a long way.

```{r, include=FALSE, echo=FALSE}
top_videos %>% 
  filter(brand_name == "Aldrich Landscape") %>% 
  inner_join(annotations) %>% arrange(desc(views)) %>% 
  select(link, views, sound_track)
```

```{r}
tiktok_embed("https://www.tiktok.com/@aldrichlandscape/video/6868589417318075653")
```

```{r, include=FALSE, echo=FALSE}
## Looks like no one song was particularly popular across all videos
annotations %>%
  filter(!str_detect(sound_track, "[oO]riginal [sS]ound")) %>%
  group_by(sound_track) %>%
  count() %>%
  arrange(desc(n))
```

## Is there a Recipe For the Perfect TikTok Post?

All this begs the question: is there a recipe for crafting a TikTok post that's just right?

While there obviously isn't a perfect formula for creating a viral video --- if there was, everyone would be using it! --- we did study the tone, style, and content of the top 5 videos from each brand to get a identify the common traits shared by the most successful TikTok videos.

```{r}
mood = c("funny", "relaxing", "suspenseful", "challenge_adventure")

content = c("shows_product", "call_to_action", "tutorial", "promotes_brand_event", "listicle", "shows_staff", "features_influencer", "features_celebrity", "features_animal", "uses_sex", "dancing", "conversation")

style = c("onScreen_text", "emojis", "graphics_overlay", "animated")
```

```{r}
count_values = function(col_name, df) {
  df %>%
    filter_at(c(col_name), ~.==TRUE) %>%
    count(name=col_name)
}

joined_annotations = annotations %>%
    inner_join(top_videos, by="link")

recipe_counts = bind_cols(map(boolean_cols, count_values, joined_annotations)) %>%
  pivot_longer(everything(), names_to="video_type", values_to="count") %>%
  mutate(count = 100 * count/dim(joined_annotations)[1]) %>%
  arrange(desc(count)) %>% 
  mutate(id = row_number())

circular_df_1 = recipe_counts  %>%
  head(10) # Keep this or not?


circular_df_1$label_text = sapply(circular_df_1$video_type, switch,
  shows_product="a product",
  onScreen_text="on-screen text",
  funny="funny content",
  features_influencer="an influencer",
  features_celebrity="a celebrity",
  suspenseful="suspense",
  animated="animation",
  dancing="dancing",
  tutorial="a tutorial",
  conversation="a conversation",
  challenge_adventure="adventure",
  promotes_brand_event="a brand event",
  relaxing="a relaxing feeling",
  features_animal="an animal",
  emojis="emojis",
  shows_staff="the brand's employees",
  graphics_overlay="a graphic overlay",
  call_to_action="a call to action",
  uses_sex="sexuality",
  listicle="a listicle"
)
```

```{r}
# data2 = bind_cols(map(boolean_cols, count_values, joined_annotations)) %>%
#     mutate_all(~100 * ./dim(joined_annotations)[1]) %>% 
#     pivot_longer(everything(), names_to="video_type", values_to="count")

# data2$label_text = sapply(data2$video_type, switch,
#   shows_product="a product",
#   onScreen_text="on-screen text",
#   funny="funny content",
#   features_influencer="an influencer",
#   features_celebrity="a celebrity",
#   suspenseful="suspense",
#   animated="animation",
#   dancing="dancing",
#   tutorial="a tutorial",
#   conversation="a conversation",
#   challenge_adventure="adventure",
#   promotes_brand_event="a brand event",
#   relaxing="a relaxing feeling",
#   features_animal="an animal",
#   emojis="emojis",
#   shows_staff="the brand's employees",
#   graphics_overlay="a graphic overlay",
#   call_to_action="a call to action",
#   uses_sex="sexuality",
#   listicle="a listicle"
# )

# data2 = data2%>%
#   arrange(desc(count)) %>%
#   head(10) %>%
#   select(label_text, count) %>%
#   pivot_wider(names_from="label_text", values_from="count")
# 
# data2 = rbind(rep(100, 20), rep(0, 20), data2)
# 
# radar_chart_1 = radarchart(data2,
#   axistype=1, 
#   pcol=rgb(0.2,0.5,0.5,0.9), 
#   pfcol=rgb(0.2,0.5,0.5,0.5), 
#   plwd=4,
#   cglcol="grey", 
#   cglty=1, 
#   axislabcol="grey", 
#   caxislabels=c("0%", "25%", "50%", "75%", "100%"),
#   cglwd=0.8,
#   vlcex=0.8 
# )

# labels = circular_df_1 %>%
#   mutate(angle = 90 - 360 *(id - 0.5) / nrow(circular_df_1)) %>%
#   mutate(hjust = ifelse(angle < -90, 1, 0)) %>%
#   mutate(angle = ifelse(angle < -90, angle+180, angle))
# 
# circular_plot_1 = circular_df_1 %>%
#   ggplot(aes(x=as.factor(id), y=count)) +
#     geom_bar(stat="identity", fill=alpha("blue", 0.3)) +
#     ylim(-30,110) +
#     theme_minimal() +
#     theme(
#       axis.text = element_blank(),
#       axis.title = element_blank(),
#       panel.grid = element_blank(),
#       plot.margin = unit(rep(-1,4), "cm")
#     ) +
#     coord_polar(start = 0) +
#     geom_text(
#       data=labels, 
#       aes(x=id, y=count+5, label=label_text, hjust=hjust), 
#       color="black", 
#       fontface="bold",
#       alpha=0.6, 
#       size=2.5, 
#       inherit.aes = FALSE
#     ) +
#     ggtitle("% of Videos With...")

bar_chart_1 = circular_df_1 %>%
  arrange(count) %>%
  mutate(label_text=factor(label_text, levels=label_text)) %>%
  ggplot(aes(x=label_text, y=count)) +
    geom_segment( aes(xend=label_text, yend=0)) +
    geom_point( size=4, color="orange") +
    coord_flip() +
    scale_y_continuous(
      labels=c("0%", "25%", "50%", "75%", "100%"),
      breaks=c(0, 25, 50, 75, 120),
      expand=c(0, 5)
    ) +
    labs(
      title="Over 90% of the videos had product placement",
      y=NULL,
      x="videos with..."
    )

# radar_chart_1
# circular_plot_1
bar_chart_1
```

As you'd expect from brands, an overwhelming majority of their posts showcase one or more products. In fact, over **90% of the videos we studied had some form of brand placement**.

So, don't feel shy about advertising your brand and your product in your posts. After all, that's the whole point of social media marketing!

Here's a great example of product placement from Pizza Hut, which earned the brand over 64 million views:

```{r}
tiktok_embed("https://www.tiktok.com/@pizzahut/video/6907646149507730693")
```

51% of the videos also had on-screen text, while a little over **30% of the videos tried to be funny**.

Celebrity and influencer endorsements are also relatively popular among TikTok brands with around a quarter of the videos featuring either an endorsement or a collaboration.

Only 3.7% of the videos included a call to action, a significant missed opportunity in our opinion. Asking your followers to follow your channel or reach out to you on other social media channels can do wonders and should always be something you consider when planning your videos.

[**TODO:** long line of text. Maybe embed a video with a good CTA here?]

Interestingly, sexual content was few and far better. Only 6 of the nearly 650 videos we analyzed employed some form of overt or subtle sexuality, with 5 of these coming from the same account (Victoria's secret).

As they say, though, sex sells. Even though the number of videos employing sexuality was small, the average number of views on these videos were extraordinary, with an average of 13.4 million views per post.

Those numbers make sexuality the second biggest attention grabber among all the types of content we considered.

[**TODO for Abhilash:** which plot do you prefer?]

```{r}
input_df = annotations %>%
    inner_join(top_videos, by="link")

count_avg_views_for_bool_cols = function(col_name, df) {
  df %>%
    filter_at(col_name, ~. == TRUE) %>%
    summarise("{col_name}" := mean(views))
}

avg_views_per_bool_col = bind_cols(
  map(boolean_cols, count_avg_views_for_bool_cols, input_df)
) %>%
  pivot_longer(everything(), names_to="video_type", values_to="avg_views") %>%
  arrange(desc(avg_views)) %>%
  mutate(avg_views_mils = avg_views/1e6) %>%
  mutate(id = row_number())

circular_df_2 = avg_views_per_bool_col %>%
  head(10)

circular_df_2$label_text = sapply(circular_df_2$video_type, switch,
  shows_product="a product",
  onScreen_text="on-screen text",
  funny="funny content",
  features_influencer="an influencer",
  features_celebrity="a celebrity",
  suspenseful="suspense",
  animated="animation",
  dancing="dancing",
  tutorial="a tutorial",
  conversation="a conversation",
  challenge_adventure="adventure",
  promotes_brand_event="a brand event",
  relaxing="a relaxing feeling",
  features_animal="an animal",
  emojis="emojis",
  shows_staff="the brand's employees",
  graphics_overlay="a graphic overlay",
  call_to_action="a call to action",
  uses_sex="sexuality",
  listicle="a listicle"
)
```

```{r}
# labels = circular_df_2 %>%
#   mutate(angle = 90 - 360 *(id - 0.5) / nrow(circular_df_2)) %>%
#   mutate(hjust = ifelse(angle < -90, 1, 0)) %>%
#   mutate(angle = ifelse(angle < -90, angle+180, angle))
# 
# circular_plot_2 = circular_df_2 %>%
#   ggplot(aes(x=as.factor(id), y=avg_views_mils)) +
#     geom_bar(stat="identity", fill=alpha("blue", 0.3)) +
#     ylim(-10,25) +
#     theme_minimal() +
#     theme(
#       axis.text = element_blank(),
#       axis.title = element_blank(),
#       panel.grid = element_blank(),
#       plot.margin = unit(rep(-1,4), "cm")
#     ) +
#     coord_polar(start = 0) +
#     geom_text(
#       data=labels, 
#       aes(x=id, y=avg_views_mils+2, label=label_text, hjust=hjust), 
#       color="black", 
#       fontface="bold",
#       alpha=0.6, 
#       size=2.5, 
#       inherit.aes = FALSE
#     ) +
#     ggtitle("Average number of views (millions) for posts with ...")

bar_chart_2 = circular_df_2 %>%
  arrange(avg_views_mils) %>%
  mutate(label_text=factor(label_text, levels=label_text)) %>%
  ggplot(aes(x=label_text, y=avg_views_mils)) +
    geom_segment(aes(xend=label_text, yend=0)) +
    geom_point(size=4, color="orange") +
    coord_flip() +
    labs(
      title="Brand events generate the most views",
      y="Avg. views (millions)",
      x="videos with..."
    )

bar_chart_2
# circular_plot_2
```

The posts which drew the largest numbers of eyeballs, though, were those which featured promotions for a brand event.

Remember how the 5 of the top 10 videos were studied were all from TikTok? Well, every single one of them drew more than 100 million views and they were all about promoting promoting an upcoming event!

As with product placement, don't shy away from publicizing your upcoming brand events on TikTok. Not only are many of the most successful TikTok brands doing just that but it seems like fans also love watching these posts.

Here's a great example of an event promotion post from TikTok's own account. It's got great music, a collab with an influencer, and even includes a helpful tutorial that people can follow if they want to participate.

```{r}
tiktok_embed("https://www.tiktok.com/@tiktok/video/6906565862132698370")
```

And it's for a good cause; no wonder it generated 129 million views!

Videos that include animals (or animal mascots) also do rather well on TikTok. For example, one of the top 10 most viewed videos among the 650 we studied is this joyful little bit with the Indianapolis Colts' mascot, Blue, giving folks a taste of some pie:

```{r}
tiktok_embed("https://www.tiktok.com/@blue/video/6797517710206029061")
```

The San Diego Zoo, too, has an extremely popular channel, often generating millions of views per post. Here's one of a kea putting my intelligence to shame:

```{r}
tiktok_embed("https://www.tiktok.com/@sandiegozoo/video/6819753891236728069")
```

Videos with graphic overlays, animations, and tutorials also do quite well on the platform.

And if you're a brand, don't shy away from turning the lens on your employees (with their consent, of course).

Among the posts we studied, videos that showed a company's staff had, on average, over 9 million views.

These videos also put a human face to your firm, which is always priceless.

This video from Starbucks, which earned 11.6 million views, is a great exhibit of the company's employees and their devotion to giving their customers the best service, no matter what:

```{r}
tiktok_embed("https://www.tiktok.com/@starbucks/video/6899106767947533574 ")
```

## Conclusion

[**TODO:** Add a link to methodology. Since we didn't create a separate data report for this study, that's something that requires some thought. Need to consult with Daniel on this.]

If you've found this guide useful, we'd love it if you could share it with your friends and colleagues who are looking to leverage TikTok for their brands. For those that want to learn more about how we conducted this research, here's a link to our methods and the raw data used for this analysis.

What was your \#1 takeaway from this guide? Let us in the comments below!

## Key Takeaways

-   **50% of the top brands we studied had no TikTok presence**, including billion-dollar brands like Google, Facebook, YouTube, and IKEA.
-   The best-performing TikTok brands **post `r round(avg_posts_summary$mean_weekly_posts, 2)` times per week** on average.
-   A **1% increase in followers corresponds to a `r fans_avg_views_slope`% increase in average views per post**.
-   **80% of the top videos had music**, with upbeat songs being the most popular music choice by far.
-   Tech, Gaming, and Media brands have the **highest average views per video**.
-   Among the brands we studied, **So Satisfying, Samsung, TikTok, Chevrolet, and Flighthouse were the 5 most popular brands** in terms of average views per video.
-   **5 of the top 10 videos** were created by TikTok itself.
-   **90% of the videos** we studied had product placement, while **30% of the videos employed humour**.
-   Approximately **25% of the videos featured either a celebrity or an influencer**.
-   **Videos promoting brand events drew nearly 20 million views**, while those featuring some form of sexuality or animals also generated well over 10 million views.
-   Video descriptons had X hashtags on average.

## TODO

1.  Add more takeaways
2.  Add Top 10 brands to Tech, Food, and Gaming [GRAPH]
3.  Add link in conclusion section.

## Not Possible

-   There should be a section on the top 10 most followed TikTok brand accounts **and the kind of content they predominantly do** [Top 10 brands have been added to the Tech, Food, and Gaming section, but the kind of content they do is difficult to achieve without analyzing a lot more than just 5 videos.]
-   How many of these brands are reposting content and what is the distribution like [Would require scraping all TikTok videos, which is a LOT of work.]
